---
title: "Module 4 exercises: dplyr demo"
author: FirstName LastName
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
# Set knitr options
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)
# Load packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(lubridate))
```

The `presidential` dataset comes with `ggplot2`, so running the above setup code block should load it automatically.

```{r test-presidential-output, eval = FALSE, include = FALSE}
# Try running me inside RStudio Server!
View(presidential)
```

## `select` demo

`select` example 1:

```{r select-example-1}
# code starts below

```

`select` example 2:

```{r select-example-2}
# code starts below

```

`select` example 3:

```{r select-example-3}
# code starts below

```

`select` example 4:

```{r select-example-4}
# code starts below

```

## `arrange` demo

`arrange` example 1:

```{r arrange-example-1}
# code starts below

```

`arrange` example 2:

```{r arrange-example-2}
# code starts below

```

## `slice` demo

`slice` example 1:

```{r slice-example-1}
# code starts below

```

`slice` example 2:

```{r slice-example-2}
# code starts below

```

`slice` example 3:

```{r slice-example-3}
# code starts below

```

## `filter` demo

`filter` example 1:

```{r filter-example-1}
# code starts below

```

`filter` example 2:

```{r filter-example-2}
# code starts below

```

`filter` example 3:

```{r filter-example-3}
# code starts below

```

`filter` example 4:

```{r filter-example-4}
# code starts below

```

`filter` example 5:

```{r filter-example-5}
# code starts below

```

`filter` example 6:

```{r filter-example-6}
# code starts below

```

## `mutate()` demo

`mutate` example 1:

```{r mutate-example-1}
# code starts below

```

`mutate` example 2:

```{r mutate-example-2}
# code starts below

```

`mutate` example 3:

```{r mutate-example-3}
# code starts below

```

## `group_by` and `summarize` demo

`summarize` example:

```{r summarize-example}
# code starts below

```

`group_by` and `summarize` example:

```{r group-by-summarize-example}
# code starts below

```

Using `write_csv` to save `elected_pres2` to disk:

```{r write-csv-file}
# code starts below

```

How to use the csv file you just saved:

```{r load-csv-file}
# code starts below

```
