Title: Module 6 – Data distributions
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2019-01-06 00:00
Tags: class notes
Slug: module06-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
icon_pen <- '<i class="fa fa-pen-square" data-fa-transform="grow-16"></i>&nbsp;'
icon_book <- '<i class="fa fa-book" data-fa-transform="grow-16"></i>&nbsp;'
icon_github <- '<i class="fab fa-github-alt" data-fa-transform="grow-8"></i>&nbsp;'
icon_pencil <- '<i class="fas fa-pencil-alt" data-fa-transform="grow-16"></i>&nbsp;'
icon_laptop <- '<i class="fa fa-laptop" data-fa-transform="grow-16"></i>&nbsp;'
```

[Readings]{.h2}

::: {.no-bullets}
*   [`r icon_book` &nbsp; [Reading 6]{.card-downloads-format}][reading06]
:::

<div style="margin-bottom: 1em"></div>

[Module exercises]{.h2}

::: {.no-bullets}
*   [`r icon_laptop` &nbsp; [Module 6 exercises]{.card-downloads-format}][module06-exercises]
:::

<div style="margin-bottom: 1em"></div>

[Homeworks]{.h2}

::: {.no-bullets}
*   [`r icon_pen` &nbsp; [Mini-homework 6 -- Analyzing data distributions]{.card-downloads-format}][mini-homework06]
:::

<div style="margin-bottom: 1em"></div>

[Videos]{.h2}

::::: {.videos-container}
::: {.video-item}
**01 - Quantifying data distributions**

```{r data-distributions-01-quantifying-data-distributions, echo = FALSE}
vembedr::embed_youtube(id = "BL5Bt-nI22k", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
**02 - Quantifying data distributions in R**

```{r data-distributions-02-quantifying-data-distributions-in-r, echo = FALSE}
vembedr::embed_youtube(id = "tvUw91TrWO4", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
**03 - Probability mass functions**

```{r data-distributions-03-probability-mass-functions, echo = FALSE}
vembedr::embed_youtube(id = "xbLim5imqe4", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
**04 - Cumulative distribution functions**

```{r data-distributions-04-cumulative-distribution-functions, echo = FALSE}
vembedr::embed_youtube(id = "WC3YL8Npujw", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::
:::::

[Slides]{.h2}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [01 - Quantifying data distributions]{.card-downloads-format}][slides-01]

*   [`r icon_pdf` &nbsp; [02 - Quantifying data distributions in R]{.card-downloads-format}][slides-02]

*   [`r icon_pdf` &nbsp; [03 - Probability mass functions]{.card-downloads-format}][slides-03]

*   [`r icon_pdf` &nbsp; [04 - Cumulative distribution functions]{.card-downloads-format}][slides-04]
:::

[slides-01]:          https://drive.google.com/file/d/1qFdt0Ez0Kxx60ezagxPigAzVy9-0rz6F
[slides-02]:          https://drive.google.com/file/d/12MAGIstBk9ByFzeuEHLRlI1TuOBCxjKL
[slides-03]:          https://drive.google.com/file/d/19gZOZ-ul_W8AXk_Kox4EKejK5-v0s4G1
[slides-04]:          https://drive.google.com/file/d/1dZq6RO87RAJKU3rHoBvuhYDi0YxvFp9p
[reading06]:          /assignments/reading06/
[mini-homework06]:    /assignments/minihw06-analyzing-data-distributions/
[module06-exercises]: /assignments/module06-exercises/
