Title: Module 3 – Data visualization
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2019-01-03 00:00
Tags: class notes
Slug: module03-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
icon_pen <- '<i class="fa fa-pen-square" data-fa-transform="grow-16"></i>&nbsp;'
icon_book <- '<i class="fa fa-book" data-fa-transform="grow-16"></i>&nbsp;'
icon_github <- '<i class="fab fa-github-alt" data-fa-transform="grow-8"></i>&nbsp;'
icon_pencil <- '<i class="fas fa-pencil-alt" data-fa-transform="grow-16"></i>&nbsp;'
icon_laptop <- '<i class="fa fa-laptop" data-fa-transform="grow-16"></i>&nbsp;'
```

[Readings]{.h2}

::: {.no-bullets}
*   [`r icon_book` &nbsp; [Reading 3]{.card-downloads-format}][reading03]
:::

<div style="margin-bottom: 1em"></div>

[Homeworks]{.h2}

::: {.no-bullets}
*   [`r icon_pen` &nbsp; [Mini-homework 3 -- Visualization by example]{.card-downloads-format}][mini-homework03]

*   [`r icon_pencil` &nbsp; [Homework 1 -- Rail trail]{.card-downloads-format}][homework01]
:::

<div style="margin-bottom: 1em"></div>

[Videos]{.h2}

::::: {.videos-container}
::: {.video-item}
**01 - Data visualization as communication**

```{r data-visualization-01-communication, echo = FALSE}
vembedr::embed_youtube(id = "tHEVRahx0WE", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
**02 - Examining numerical data**

```{r data-visualization-02-examining-numerical-data, echo = FALSE}
vembedr::embed_youtube(id = "z9Xe3IfkNQU", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
**03 - Describing visualizations**

```{r data-visualization-03-describing, echo = FALSE}
vembedr::embed_youtube(id = "p6J9IxSBMwo", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
**04 - Data visualization with ggplot2**

```{r data-visualization-04-data-visualization-with-ggplot2, echo = FALSE}
vembedr::embed_youtube(id = "Wx-Kr9cp7O8", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::
:::::

[Slides]{.h2}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [01 - Data visualization as communication]{.card-downloads-format}][slides-01]

*   [`r icon_pdf` &nbsp; [02 - Examining numerical data]{.card-downloads-format}][slides-02]

*   [`r icon_pdf` &nbsp; [03 - Describing visualizations]{.card-downloads-format}][slides-03]

*   [`r icon_pdf` &nbsp; [04 - Data visualization with ggplot2]{.card-downloads-format}][slides-04]
:::

[slides-01]:        https://drive.google.com/file/d/1VK_vXEHBK5U35rfgetwon07A7YLpaj_H
[slides-02]:        https://drive.google.com/file/d/1KiY4qavGUf3gMQF5rg1cR5HzmaI9i0dQ
[slides-03]:        https://drive.google.com/file/d/1zVbreifnXfsTiPiTNnQoacOPvtwG-aLN
[slides-04]:        https://drive.google.com/file/d/1iOh3_7T7hhCO3IWkSoXCT1xqQUUHc0hw
[reading03]:        /assignments/reading03/
[homework01]:       /assignments/homework-1/
[mini-homework03]:  /assignments/minihw03-visualization-by-example/
