Title: Module 7 – Inference and simulation
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2019-01-07 00:00
Tags: class notes
Slug: module07-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
icon_pen <- '<i class="fa fa-pen-square" data-fa-transform="grow-16"></i>&nbsp;'
icon_book <- '<i class="fa fa-book" data-fa-transform="grow-16"></i>&nbsp;'
icon_github <- '<i class="fab fa-github-alt" data-fa-transform="grow-8"></i>&nbsp;'
icon_pencil <- '<i class="fas fa-pencil-alt" data-fa-transform="grow-16"></i>&nbsp;'
icon_laptop <- '<i class="fa fa-laptop" data-fa-transform="grow-16"></i>&nbsp;'
```

[Readings]{.h2}

::: {.no-bullets}
*   [`r icon_book` &nbsp; [Reading 7]{.card-downloads-format}][reading07]
:::

<div style="margin-bottom: 1em"></div>

[Homeworks]{.h2}

::: {.no-bullets}
*   [`r icon_pen` &nbsp; [Mini-homework 7 -- Who busts the Mythbusters?]{.card-downloads-format}][mini-homework07]

*   [`r icon_pencil` &nbsp; [Homework 3 -- National Survey of Family Growth]{.card-downloads-format}][homework03]
:::

<div style="margin-bottom: 1em"></div>

[Videos]{.h2}

::::: {.videos-container}
::: {.video-item}
<p style="height: 50px">**01 - Gender discrimination case study**</p>

```{r inference-and-simulations-01-gender-discrimination-case-study, echo = FALSE}
vembedr::embed_youtube(id = "EL9bbzblRq8", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
<p style="height: 50px">**02 - A hypothesis test as a court trial**</p>

```{r inference-and-simulations-02-a-hypothesis-test-as-a-court-trial, echo = FALSE}
vembedr::embed_youtube(id = "LzsLhuxYiMs", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
<p style="height: 50px">**03 - A manual simulation of the gender discrimination experiment**</p>

```{r inference-and-simulations-03-a-manual-simulation-of-the-gender-discrimination-experiment, echo = FALSE}
vembedr::embed_youtube(id = "hjVjAzuMRDM", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
<p style="height: 50px">**04 - Simulating the gender discrimination experiment in R**</p>

```{r inference-and-simulations-04-simulating-the-gender-discrimination-experiment-in-r, echo = FALSE}
vembedr::embed_youtube(id = "8wQ-uU611vI", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::
:::::

[Slides]{.h2}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [01 - Gender discrimination case study]{.card-downloads-format}][slides-01]

*   [`r icon_pdf` &nbsp; [02 - A hypothesis test as a court trial]{.card-downloads-format}][slides-02]

*   [`r icon_pdf` &nbsp; [03 - A manual simulation of the gender discrimination experiment]{.card-downloads-format}][slides-03]

*   [`r icon_pdf` &nbsp; [04 - Simulating the gender discrimination experiment in R]{.card-downloads-format}][slides-04]

*   [`r icon_pdf` &nbsp; [05 - One-sided hypothesis tests using infer]{.card-downloads-format}][slides-05]

*   [`r icon_pdf` &nbsp; [06 - Two-sided hypothesis tests using infer]{.card-downloads-format}][slides-06]

*   [`r icon_pdf` &nbsp; [07 - Variability of estimates and confidence intervals]{.card-downloads-format}][slides-07]

*   [`r icon_pdf` &nbsp; [08 - Simulating the confidence interval]{.card-downloads-format}][slides-08]

*   [`r icon_pdf` &nbsp; [09 - Effect size]{.card-downloads-format}][slides-09]
:::

[slides-01]:          https://drive.google.com/file/d/1du9nvutPgGqmhIk8IwGTTDbtg7MFTNWY 
[slides-02]:          https://drive.google.com/file/d/1k9upa_hsq7-jUFwdqCFAq6bpenHKaytT
[slides-03]:          https://drive.google.com/file/d/1c3ikTCXhWEeT5pkuSPVxDjzz3x1BdQhp
[slides-04]:          https://drive.google.com/file/d/1N7tV39N7mocfWuxWhetPIxfWCc_um4lT
[slides-05]:          https://drive.google.com/file/d/1SUewphETMnIvzhbXoKK5mXQXhRxpLxhv
[slides-06]:          https://drive.google.com/file/d/1K8UbNKFCYUmOD73xmpxe2NdZ8pMIzmns
[slides-07]:          https://drive.google.com/file/d/1-drQTqeRPJOBSuJHX9HWtpof_g0OO1gh 
[slides-08]:          https://drive.google.com/file/d/19IpyKCWJhFiaO3bndDip3DnAewyZZ5Ea
[slides-09]:          https://drive.google.com/file/d/1IjnRZ9Q-wSlWyUDoJ6flyxZidThAdXE5
[reading07]:          /assignments/reading07/
[homework03]:         /assignments/homework-3/
[mini-homework07]:    /assignments/minihw07-who-busts-the-mythbusters/
