Title: Module 1 – What are the computational and data sciences?
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2019-01-01 00:00
Tags: class notes
Slug: module01-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
icon_pen <- '<i class="fa fa-pen-square" data-fa-transform="grow-16"></i>&nbsp;'
icon_book <- '<i class="fa fa-book" data-fa-transform="grow-16"></i>&nbsp;'
icon_github <- '<i class="fab fa-github-alt" data-fa-transform="grow-8"></i>&nbsp;'
icon_pencil <- '<i class="fas fa-pencil-alt" data-fa-transform="grow-16"></i>&nbsp;'
icon_laptop <- '<i class="fa fa-laptop" data-fa-transform="grow-16"></i>&nbsp;'
```

[Readings]{.h2}

::: {.no-bullets}
*   [`r icon_book` &nbsp; [Reading 1]{.card-downloads-format}][reading01]
:::

<div style="margin-bottom: 1em"></div>

[Module exercises]{.h2}

::: {.no-bullets}
*   [`r icon_laptop` &nbsp; [Module 1 exercises]{.card-downloads-format}][module-exercises]
:::

<div style="margin-bottom: 1em"></div>

[Homeworks]{.h2}

::: {.no-bullets}
*   [`r icon_pen` &nbsp; [Mini-homework 1]{.card-downloads-format}][mini-homework01]
:::

<div style="margin-bottom: 1em"></div>

[Videos]{.h2}

::::: {.videos-container}
::: {.video-item}
**01 - What are the computational and data sciences - Science**

```{r what-are-comput-data-sci-02-science, echo = FALSE}
vembedr::embed_youtube(id = "fxLFfuW4eag", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
**02 - What are the computational and data sciences - Data Overview**

```{r what-are-comput-data-sci-03-data-overview, echo = FALSE}
vembedr::embed_youtube(id = "t7iEMTkfY6g", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
**03 - What are the computational and data sciences - Data Sampling**

```{r what-are-comput-data-sci-04-data-sampling, echo = FALSE}
vembedr::embed_youtube(id = "kGlrYxTDGh8", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
**04 - What are the computational and data sciences - Computation**

```{r what-are-comput-data-sci-05-computation, echo = FALSE}
vembedr::embed_youtube(id = "7mhehSq959k", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::
:::::

[Slides]{.h2}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [01 - Science]{.card-downloads-format}][slides-01]

*   [`r icon_pdf` &nbsp; [02 - Data overview]{.card-downloads-format}][slides-02]

*   [`r icon_pdf` &nbsp; [03 - Data sampling]{.card-downloads-format}][slides-03]

*   [`r icon_pdf` &nbsp; [04 - Computation]{.card-downloads-format}][slides-04]
:::

[slides-01]:        https://drive.google.com/file/d/1X2Aq6xBlv7mE4QjSF1WNigtw_xhudggE
[slides-02]:        https://drive.google.com/file/d/1Q9aNKZRnjzY-fUoEICQ0eg2bxMoMkgRU
[slides-03]:        https://drive.google.com/file/d/1qInq4DXzYsHjmnw2lVu_ffVrAUuzN5ko
[slides-04]:        https://drive.google.com/file/d/1HAZiWrMGi8KUC1aStF7Gt-9nphjhfAs8
[reading01]:        /assignments/reading01/
[mini-homework01]:  /assignments/minihw01-can-twitter-predict-election-results/
[module-exercises]: /assignments/module01-exercises/
