Title: Module 5 – Data reshaping
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2019-01-05 00:00
Tags: class notes
Slug: module05-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
icon_pen <- '<i class="fa fa-pen-square" data-fa-transform="grow-16"></i>&nbsp;'
icon_book <- '<i class="fa fa-book" data-fa-transform="grow-16"></i>&nbsp;'
icon_github <- '<i class="fab fa-github-alt" data-fa-transform="grow-8"></i>&nbsp;'
icon_pencil <- '<i class="fas fa-pencil-alt" data-fa-transform="grow-16"></i>&nbsp;'
icon_laptop <- '<i class="fa fa-laptop" data-fa-transform="grow-16"></i>&nbsp;'
```

[Readings]{.h2}

::: {.no-bullets}
*   [`r icon_book` &nbsp; [Reading 5]{.card-downloads-format}][reading05]
:::

<div style="margin-bottom: 1em"></div>

[Module exercises]{.h2}

::: {.no-bullets}
*   [`r icon_laptop` &nbsp; [Module 5 exercises]{.card-downloads-format}][module05-exercises]
:::

<div style="margin-bottom: 1em"></div>

[Homeworks]{.h2}

::: {.no-bullets}
*   [`r icon_pen` &nbsp; [Mini-homework 5 -- Tidy Gradebook]{.card-downloads-format}][mini-homework05]
:::

<div style="margin-bottom: 1em"></div>

[Videos]{.h2}

::::: {.videos-container}
::: {.video-item}
**01 - Principles of tidy data**

```{r data-reshaping-01-principles-of-tidy-data, echo = FALSE}
vembedr::embed_youtube(id = "FMJfjwAyMA0", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
**02 - The [gather]{.monospace} function**

```{r data-reshaping-02-the-gather-function, echo = FALSE}
vembedr::embed_youtube(id = "Hnl7Ksc3bUE", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
**03 - The [spread]{.monospace} function**

```{r data-reshaping-03-the-spread-function, echo = FALSE}
vembedr::embed_youtube(id = "VV_JdcIPVz8", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
**04 - The [separate]{.monospace} function**

```{r data-reshaping-04-the-separate-function, echo = FALSE}
vembedr::embed_youtube(id = "uqiqEnRKfFg", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::

::: {.video-item}
**05 - The [unite]{.monospace} function**

```{r data-reshaping-05-the-unite-function, echo = FALSE}
vembedr::embed_youtube(id = "izCk8NBycmo", height = 325, width = 365, allowfullscreen = TRUE, frameborder = 0)
```
:::
:::::

[Slides]{.h2}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [01 - Principles of tidy data]{.card-downloads-format}][slides-01]

*   [`r icon_pdf` &nbsp; [02 - The [gather]{.monospace} function]{.card-downloads-format}][slides-02]

*   [`r icon_pdf` &nbsp; [03 - The [spread]{.monospace} function]{.card-downloads-format}][slides-03]

*   [`r icon_pdf` &nbsp; [04 - The [separate]{.monospace} function]{.card-downloads-format}][slides-04]

*   [`r icon_pdf` &nbsp; [05 - The [unite]{.monospace} function]{.card-downloads-format}][slides-05]
:::

[slides-01]:          https://drive.google.com/file/d/174WhC51cMkM_IfBH12HME-bZNQu3rJ4o
[slides-02]:          https://drive.google.com/file/d/1CTxz65d4TfHhCAl3AaF1guNl3OvFABgm
[slides-03]:          https://drive.google.com/file/d/1c3yI5GcKdF93rALaa72jo8vV0PqyIuGW
[slides-04]:          https://drive.google.com/file/d/17SOza86ASc-ioFA6_vmFeUj_HGWv_B7t
[slides-05]:          https://drive.google.com/file/d/1En-4bj2Vh74wdkPbdRmXSSS5K0UQNFGK
[reading05]:          /assignments/reading05/
[mini-homework05]:    /assignments/minihw05-tidy-gradebook/
[module05-exercises]: /assignments/module05-exercises/
